%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Upgrading Skills}
{Sabbatical}
{Solapur, India}
{Dec 2022 - Present}
{
\begin{cvitems}
%\setlength{\itemsep}{1ex} %
\item {Voluntarily took a career break post-appraisal to address personal responsibilities.}
\item {Enhancing software engineering skills with a focus on \textit{C++, Python,} problem-solving, algorithms, data structures, and system design.}
\end{cvitems}
}

\cventry
{Senior Software Engineer} % Job title
{Qualys Security Tech Services Private Limited} % Organization
{Pune, India} % Location
{Jun 2019 - Nov 2022} % Date(s)
{
\begin{cvitems}
\setlength{\itemsep}{1ex} %
%
% ---
\item {As a senior developer for the Web Application Security \textit{(WAS)} product, led development initiatives while demonstrating proficiency in \textit{C++}.}
%\item {Incorporated Passive Scanning feature into WAS Engine}
\item {Implemented Passive Scanning feature into Web Application Security \textit{(WAS)} engine.}
    \begin{cvitemsnested}
    \item {By observing request-response identifies the technology stack utilized by website.}
    \end{cvitemsnested}
% ---
\item {Enhanced the Open Redirect detection feature in the \textit{WAS} engine.}
    \begin{cvitemsnested}
    \item {Significantly minimized false-negative detections in open redirect scenarios.}
    \item {Reduced the required number of requests for open redirect vulnerability detection.}
    \end{cvitemsnested}
% ---
\item {Integrated \textit{SSL/TLS}-related vulnerability detection into the \textit{WAS} engine.}
\item {Incorporated various minor enhancements, including support for features like subresource integrity and content security policy, in the \textit{WAS} engine.}
%\item {Addressed critical \textit{CRM} issues from clients, consistently prioritizing, fixing, and enhancing functionalities, leading to improved customer retention and acquisition of new clients.}
\item{Proactively resolved critical \textit{CRM} issues reported by clients, demonstrating a consistent commitment to prioritizing, troubleshooting, and enhancing functionalities.}
%
\end{cvitems}
}
%------------------------------------------------



\cventry
{Software Engineer} % Job title
{} % Organization
{} % Location
{Jun 2018 - Jun 2019} % Date(s)
{
\begin{cvitems}
\setlength{\itemsep}{1ex} %
%
% ---
\item {Incorporated \textit{TLS 1.3} support into \textit{WAS} engine \textit{(resolution of licensing issues)}.}
	\begin{cvitemsnested}
		\item {Upgraded \textit{OpenSSL} library version from \textit{1.0.2 to 1.1.1} in \textit{QtWebkit 4.4}.}
		\item {Made necessary changes to support new \textit{APIs} and removed deprecated \textit{APIs}.}
		\item {Ensured backwards compatibility with all previous versions of \textit{SSL/TLS} protocols.}
		%\item {Tested and validated upgraded library integration, addressing issues found}
	\end{cvitemsnested}
% ---
\item {Upgraded \textit{curl} version from \textit{7.58.0 to 7.64.0}.}
	\begin{cvitemsnested}
		\item {Made changes to support all versions of \textit{SSL/TLS} protocols from \textit{OpenSSL}.}
		\item {Made changes to support all algorithms and features from \textit{OpenSSL 1.1.1}.}
	\end{cvitemsnested}
%
\end{cvitems}
}
%------------------------------------------------
%------------------------------------------------


\cventry
{Quality Engineer Developer} % Job title
{VMware Software India Private Limited} % Organization
{Pune, India} % Location
{Nov 2014 - Jan 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Played a key role in crafting a robust test framework for scalability assessments using \textit{Python} for \textit{VMware NSX}.}
\item {Collaborated with the team to enhance the framework, resulting in expanded scalability testing that includes features such as \textit{NAT, Distributed Firewall, Routing}.}
\item {Transformed \textit{API} call execution within the framework with \textit{C++ REST SDK}, achieving a significant multifold reduction in setup time.}
\item {Automated \textit{Riak} cluster setup and cleanup for streamlined test configuration and result analysis.}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Member of Technical Staff} % Job Title
{Zlemma Analytics Pvt Ltd (Acquired by Hired Inc.)} % Organization
{Pune, India} % Location
{Nov 2013 - Jul 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Created a \textit{Django-}based web app simplifying data engineers' tasks in cleaning, correcting, and managing \textit{MySQL} databases via a user-friendly interface.}
\item {Customized an open-source web test framework to configure \textit{UI} tests across various browser versions and types, enhancing the efficiency and coverage of \textit{UI} testing.}
\end{cvitems}
}
%------------------------------------------------
\cventry
{Member Technical Staff} % Job Title
{Oracle India Private Limited} % Organization
{Bengaluru, India} % Location
{Jun 2011 - Oct 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Managed a large and intricate legacy \textit{C++} codebase \textit{(Oracle Siebel CRM)}, focusing on resolving memory management and character encoding/decoding issues.}
		\item {Key contributor to product improvement by effectively addressing reported issues from both customers and the \textit{Coverity} static analysis tool.}
	\end{cvitems}
}
%------------------------------------------------

\end{cventries}
